Deriving Multi-Headed Projective Dependency Parses from Link Grammar Parses

### 2014-11-17 doc/LinksToDAG_final.tex
added in several of reviewer 2's comments. Tried to follow Jason's suggestion of changing the tone of the paper.

\bibliographystyle{plain}

%\documentclass[11pt]{article}
%\usepackage{acl2014}
\usepackage{times}
%\usepackage{url}
%\usepackage{latexsym}
\usepackage{amsmath}
%\usepackage{xspace}
\usepackage{enumitem}
\usepackage[small]{caption}
\usepackage{longtable}

@@

% \newcommand{\root}{\texttt{\$}}

\title{Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses}
% Oriented link grammar: Creating a multi-headed dependency corpus.

\author{Juneki Hong and Jason Eisner\\
   Department of Computer Science \\
   Johns Hopkins University \\
   Baltimore, MD 21218, USA \\ 
   {\tt \{juneki,jason\}@cs.jhu.edu} \\
}

@@

\begin{abstract}
\noindent
Under multi-headed dependency grammar, a parse is a connected DAG rather than a tree.  Such formalisms can be more syntactically and semantically expressive.  However, 
it is hard to train, test, or improve multi-headed parsers because few multi-headed corpora exist, particularly for the projective case.
% OLD
% investigate the benefit of such parsers or to work on making them faster or more accurate.  
To help fill this gap, we observe that link grammar already produces {\em undirected} projective graphs.  
% OLD
% ... produces parses that are similar to multi-headed projective dependency parses, except that the links are undirected. 
We use Integer Linear Programming to assign consistent directions to the labeled links in a corpus of several thousand parses produced by the Link Grammar Parser, which has broad-coverage hand-written grammars of English as well as Russian and other languages.  We find that such directions can indeed be consistently assigned in a way that yields valid multi-headed dependency parses. The resulting parses in English appear reasonably linguistically plausible, though differing in style from CoNLL-style parses of the same sentences; we discuss the differences.  
\end{abstract}

@@

@@

Thus, we chose to use a sample of {\em actual} sentences parsed by the link grammar, and to seek a direction mapping so that {\em these} parses would not violate our constraints after directions were imposed.  If no such mapping exists, then we are willing to orient a few edge tokens in the wrong direction to ensure that the parses are still well-formed---but we minimize the number of such violations.  In this way, the empirical distribution of sentences guides our assignment of directions.  The resulting directed corpus can be used for research on multi-headed dependency parsing.

@@

We generated link parses using the AbiWord/CMU link grammar parser version 5.0.8 \cite{LINKPARSER-2014}.  The parser's coverage is not perfect: we obtained connected parses for only \input{figure/conll_analysis_sentences_total.tex}(of \input{figure/conll_analysis_sentences_original.tex}$\!\!$) English sentences and only \input{figure/russian_sentence_count.tex}(of \input{figure/russian_original_sentence_count.tex}$\!\!$) Russian sentences, discarding the other sentences.
These two languages have the most mature lexicons at present, although lexicons for 7 other languages are available.

The link grammar parses do differ in style from the single-headed CoNLL parses of the same English sentences.  They have \input{figure/conll_analysis_edge_percent.tex}more edges overall.  Only \input{figure/conll_analysis_precision.tex}of the links match CoNLL arcs, and only \input{figure/conll_analysis_recall.tex}of the CoNLL arcs match links.
% DATA FOR THE ABOVE
% \begin{figure}[ht!]
%   \centering
%   \small
%   \input{figure/conll_analysis_arcs.tex}
%   \caption{Arcs that match links}
% \end{figure}
% 
% OLD
% Using the sentences of the dependency corpus as comparison, we find that the link parses do not wholly subsume dependency parses, and that the undirected links match roughly three fourths of the arcs in the conll dependency corpus. \todo{This is because...}

@@

%\newpage
\begin{bibliography}{LinksToDAG_final}

%\bibliographystyle{acl2014}
%\bibliography{LinksToDAG}
\end{bibliography}

>>>>

\bibliographystyle{plain}
%\bibliographystyle{acl2014}

%\documentclass[11pt]{article}
%\usepackage{acl2014}
\usepackage{times}
%\usepackage{url}
%\usepackage{latexsym}
\usepackage{amsmath}

%\usepackage{xspace}
\usepackage{enumitem}
\usepackage[small]{caption}
\usepackage{longtable}

@@

\title{Deriving Multi-Headed Projective Dependency Parses from Link Grammar Parses}
% Oriented link grammar: Creating a multi-headed dependency corpus.

\author{Juneki Hong and Jason Eisner
  \\[0.5cm] Department of Computer Science
  \\Johns Hopkins University
  \\Baltimore, MD 21218, USA 
  \\{\tt \{juneki,jason\}@cs.jhu.edu}
}

@@

\begin{abstract}
\noindent
Under multi-headed dependency grammar, a parse is a connected DAG rather than a tree.  Such formalisms can be more syntactically and semantically expressive.  However, 
it is hard to train, test, or improve multi-headed parsers because few multi-headed corpora exist, particularly for the projective case.
% OLD
% investigate the benefit of such parsers or to work on making them faster or more accurate.  
To help fill this gap, we observe that link grammar already produces {\em undirected} projective graphs, and so we wanted to determine whether these could be converted into directionalized dependency parses.
% OLD
% ... produces parses that are similar to multi-headed projective dependency parses, except that the links are undirected. 
We use Integer Linear Programming to assign consistent directions to the labeled links in a corpus of several thousand parses produced by the Link Grammar Parser, which has broad-coverage hand-written grammars of English as well as Russian and other languages.  We find that such directions can indeed be consistently assigned in a way that yields valid multi-headed dependency parses. 
%The resulting parses in English appear reasonably linguistically plausible, though differing in style from CoNLL-style parses of the same sentences; we discuss the differences.  
However, the resulting parses in English differ in style from CoNLL-style parses of the same sentences; we discuss the differences.

\end{abstract}

@@

%\newpage

@@

% OLD
% Thus, we chose to use a sample of {\em actual} sentences parsed by the link grammar, and to seek a direction mapping so that {\em these} parses would not violate our constraints after directions were imposed.  
Thus, we chose to use a sample of sentences sucessfully parsed by the link grammar, and to seek a direction mapping that would not violate our constraints after directions were imposed.
If no such mapping exists, then we are willing to orient a few edge tokens in the wrong direction to ensure that the parses are still well-formed---but we minimize the number of such violations.  In this way, the empirical distribution of sentences guides our assignment of directions.  The resulting directed corpus could be used for research on multi-headed dependency parsing.

@@

We generated link parses using the AbiWord/CMU link grammar parser version 5.0.8 \cite{LINKPARSER-2014}.  The parser's coverage is not perfect: we obtained connected parses for only \input{figure/conll_analysis_sentences_total.tex}(of \input{figure/conll_analysis_sentences_original.tex}$\!\!$) English sentences and only \input{figure/russian_sentence_count.tex}(of \input{figure/russian_original_sentence_count.tex}$\!\!$) Russian sentences, discarding the other sentences\footnote{When the link parser fails, it outputs a disconnected graph representing its best effort parse within a timelimit. We removed these sentences because our ILP encoding tries to satisfy the edges of an entire connected parse. Given a solution, it would be possible to return to these disconnected parses, directionalize the edges, and include them along with the rest of the corpus. It would also be possible to include these sentences for the ILP to solve by modifying the ILP to satisfy the edges of all disconnected components of a parse.}
These two languages have the most mature lexicons at present, although lexicons for 7 other languages are available.

The link grammar parses differ in style from the single-headed CoNLL parses of the same English sentences, and the multiheaded arcs are used sparingly with only \input{figure/conll_analysis_edge_percent.tex}more edges overall.  Only \input{figure/conll_analysis_precision.tex}of the links match CoNLL arcs, and only \input{figure/conll_analysis_recall.tex}of the CoNLL arcs match links.
% DATA FOR THE ABOVE
% \begin{figure}[ht!]
%   \centering
%   \small
%   \input{figure/conll_analysis_arcs.tex}
%   \caption{Arcs that match links}
% \end{figure}
% 
% OLD
% Using the sentences of the dependency corpus as comparison, we find that the link parses do not wholly subsume dependency parses, and that the undirected links match roughly three fourths of the arcs in the conll dependency corpus. \todo{This is because...}

@@

%\newpage

\begin{bibliography}{LinksToDAG_final}

%\bibliographystyle{acl2014}

%\bibliography{LinksToDAG}
\end{bibliography}
